Møil: A web-based administration tool for mail servers backed by relational databases

### 2014-07-30 doc/study/study.tex
Missing Møil model descriptions and perspective.

			\subsubsection*{Domains}

			\subsubsection*{Mailboxes}

			\subsubsection*{Aliases}

@@

		\subsection*{Perspective}
			% Better CLI
			% Spam
			% Sieve

		\subsection*{Setup}
			% Relevant configs for postfix and dovecot
			% Setup of rails app
			% Links to README on GitHub

>>>>

			\subsubsection*{Domains}
				For \texttt{Domains} the following attributes are saved per
				record: \texttt{name} (which is the actual domain- or hostname,
				\texttt{description}, \texttt{backupmx} (indicates, if the
				domain is specified as backup MX), \texttt{active},
				\texttt{quick\_access} (indicates, if the domain edit is
				reachable through a quick access menu in the \ac{UI}),
				\texttt{mx\_set} (for automatically saving, if the MX record in
				the DNS points to the correct mail server) and the timestamps
				of creation and last update. \texttt{Domains} are connected to
				many \texttt{Mailboxes} and \texttt{Aliases} to reflect the
				affiliation of the latter.

			\subsubsection*{Mailboxes}
				A \texttt{Mailbox} is connected to its \texttt{Domain} and
				possibly also to one \texttt{Relocation} and has the attributes
				\texttt{username} (which is the part in front of the
				domain in the E-Mail address), \texttt{encrypted\_password}
				(containing the password hash), \texttt{name} (for a given name
				for example), \texttt{mail\_location} (which is empty by
				default but can be used to move the users mail data location),
				\texttt{quota}, \texttt{active}, \texttt{admin} and timestamp
				attributes for saving the date of creation or the last update.

			\subsubsection*{Aliases}
				\texttt{Aliases} represent mail forwardings and are also
				connected to their affiliated \texttt{Domain}. They have the
				attributes \texttt{username}, \texttt{goto} (which is the
				target of the forwarding and can contain one or more internal
				or external E-Mail addresses seperated by commas),
				\texttt{active}, \texttt{description} and timestamps of
				creation and last update.

@@

		\subsection*{Perspective}
			Not least through the evaluation of the different solutions for
			Open Source mail system administration user interfaces, some
			possible features for Møil become obvious.

			\begin{description}
				\item[\rm Better \ac{CLI}]\ \\
					Currently, Møil has seperate \ac{CLI} tools for the most
					important tasks like managing domains and mailboxes and
					importing data from an \emph{postfix.admin} installation.
					This can be expanded into a single \ac{CLI} utility with
					better support for the features, the web user interface
					offers.

				\item[\rm Spam and virus check integration]\ \\
					Some compared solutions integrate \texttt{amavisd-new} by
					shared database tables. After this being clear, there is
					not much left to be solved conceptually for a spam and
					virus check integration and this becomes a question of time.

				\item[\rm Support for server-side filters]\ \\
					The support for server-side filters in Møil was already
					examined and begun but at first, a Ruby library for the
					ManageSieve protocol has to be implemented, because the
					only one existing is not maintained anymore and became
					disfunctional.
			\end{description}

		\subsection*{Setup}
			\subsubsection*{Relevant configs for postfix and dovecot}

			\subsubsection*{Setup of the rails app}

			\subsubsection*{Further readings}
				% Links to README on GitHub
